---
title: "Labour Mobility Test Post. HUGE!"
author: "Jackson"
date: "2017-06-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(scales)

LabMobABS <- read.csv("https://raw.githubusercontent.com/youngstreetinitiative/brusselssproutsideas/master/Data/Labour%20Mobility%20By%20Industry.csv?token=AWGs-0kHmTZS7oyZmygIunKuHwU2rjd0ks5ZXJQ-wA%3D%3D")

LabMobIndustryABS <- read.csv("https://raw.githubusercontent.com/youngstreetinitiative/brusselssproutsideas/master/Data/LabourMobility.csv?token=AWGs-0Swr2R_efVrTtNE5FY1epy8Kuyqks5ZXJSBwA%3D%3D")

ReasonCeasedEmpABS <- read.csv("https://raw.githubusercontent.com/youngstreetinitiative/brusselssproutsideas/master/Data/Reasons%20Ceasing%20Employment.csv?token=AWGs-8buS4tZltJD7XxtdbnPkNDP_FzDks5ZXJSowA%3D%3D")

ABSLabourMobility <- merge(LabMobABS,merge(LabMobIndustryABS,ReasonCeasedEmpABS,all = T),all = T) %>%
  mutate(Date=as.Date(Date,format="%d/%m/%Y")) %>% arrange(Date)
```


## Labour Mobility in Australia from 1975-2016

The Australian Bureau of Statistics has run the Labour Mobility Survey alongside the monthly Labour Force Survey on a semi-frequent basis over the past 40 years.

The following data comes from report available [online](http://www.abs.gov.au/ausstats/abs@.nsf/mf/6209.0/)  for the years 1994 onward (as catalogue number 6209.0). Data points before 1994 come from printed reports held by the [Library of New South Wales](http://www.sl.nsw.gov.au/research-and-collections).

### Changed employer


```{r eval=T,echo=T, out.width='960px'}
ABSLabourMobility <- ABSLabourMobility %>%
  mutate(PropChangedEmp=ChangedEmp/Employed)
ggplot(subset(ABSLabourMobility,!is.na(PropChangedEmp)),aes(x=Date,y=PropChangedEmp))+
  geom_line() + 
  scale_y_continuous(limits=c(0,0.16),breaks=c(seq(0,0.16,0.02)),labels=scales::percent)+
  scale_x_date(breaks = date_breaks("2 years"),labels=date_format("%Y"))+
  ylab("Proportion of Workers Employed at Survey")+xlab("Year")

```


### Reasons left job

```{r eval=T,echo=T, out.width='960px'}
ReasonCeasedEmp <- ReasonCeasedEmpABS %>% select(-CeasedEmp) %>%
  gather(key=ReasonLeft,value=Ceased,-c(Date,EmpSomeTime)) %>%
  mutate(PropReasonLeft=Ceased/EmpSomeTime,
         Date=as.Date(Date,format="%d/%m/%Y"),
         ReasonLeft=as.factor(ReasonLeft))

ggplot(subset(ReasonCeasedEmp,ReasonLeft=="JobLoser"|ReasonLeft=="Jobleaver"),
              aes(x=Date,y=PropReasonLeft,colour=ReasonLeft))+
    geom_line() + 
    scale_y_continuous(limits=c(0,0.14),breaks=c(seq(0,0.14,0.02)),labels=scales::percent)+
    scale_x_date(breaks = date_breaks("2 years"),labels=date_format("%Y"))+
  ylab("Proportion of Workers Employed during year")+xlab("Year")
```

```{r eval=T,echo=T, out.width='960px'}
ggplot(subset(ReasonCeasedEmp,ReasonLeft!="JobLoser" & ReasonLeft!="Jobleaver"),
       aes(x=Date,y=PropReasonLeft,colour=ReasonLeft))+
  geom_line() + 
  scale_y_continuous(limits=c(0,0.1),breaks=c(seq(0,0.1,0.02)),labels=scales::percent)+
  scale_x_date(breaks = date_breaks("2 years"),labels=date_format("%Y"))+
  ylab("Proportion of Workers Employed during year")+xlab("Year")
```